### 2017-09-09 paper/related.tex
pass on related

@@

%% \Jbc{Missing work about testing in the cloud and Jon Bell}

>>>>

High-level parallelism \Fix{...}
CUT~\cite{gambi-etal-issta2017} is a tool to automatically parallelize
unit tests across a distributed environment. \Fix{...}
CUT allows the developer to control resource allocation, and deal with
the project specific test dependencies.
Important to note that high-level parallelism techniques is
complementary to test suite parallelization.

@@
